Preliminary Thesis Defence

### 2014-01-02 south-africa.tex
more intro

For example, if we measure a height $x$ for a child of age $y$ (in weeks/months),
then we refer the to WHO tables, find the relevant ideal height and standard deviation for a child of age $y$.
We then substract the ideal height ($\mu_y$) from the observed height,
and divide by the standard devation ($\sigma_y$), like so:
\[
z_{xy} = \frac{x - \mu_y}{\sigma_{y}}
\]
We distinquish between Age Based Z-scores (ABZ) and Height-Based Z-scores (HBZ).
This is described in futher detail in \autoref{sa:data:who}.

@@

@@

% ESTIMATION

Our main finding is that we find a negative effect of the policy change on the age-based growth metrics on children (HAZ and WAZ).
In the height-based metrics we find a negative effect of the state pension income of men on the body mass index (though not on the WHZ).
Our results seems to indicate that the policy change had a negative impact on the long-term growth of children.
Furthermore, we see a negative effect of the mens pension income on the BMI of children.
These results provide support for the theory that exogenous incomes in a poverty relief context,
such as CCTs and UCTs are best transfered to women in the households.

>>>>

For example, if we measure a height $x$ for a child of age $y$ (in weeks/months),
then we refer the to WHO tables, find the relevant ideal height and standard deviation for a child of age $y$.
We then substract the ideal height ($\mu_y$) from the observed height,
and divide by the standard devation ($\sigma_y$), like so:
\[
z_{xy} = \frac{x - \mu_y}{\sigma_{y}}
\]
We distinquish between Age Based Z-scores (ABZ) and Height-Based Z-scores (HBZ).
We use two types ABZs and two types of HBZs, for a total of four types of z-scores.
This is described in futher detail in \autoref{sa:data:who}.

@@

We formulate three models. One without the treatment dummy,
one with the treatment dummy, and one with the treatment dummy,
and an interaction term with male pension recipient status.
Each of these models is estimated with all four types of z-scores,
which gives a total of twelve estimation equations.

@@

Our main finding is a negative effect of the policy change on the age-based growth metrics on children (HAZ and WAZ).
In the height-based metrics we find a negative effect of the state pension income of men on the body mass index (though not on the WHZ).
Our results seems to indicate that the policy change had a negative impact on the long-term growth of children.
Furthermore, we see a negative effect of the mens pension income on the BMI of children.
These results provide support for the theory that exogenous incomes in a poverty relief context,
such as CCTs and UCTs are best transfered to women in the households.
